Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-09 paper/appendices.tex
Edits to paper

@@

Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints. Here we outline two additional models, the nearly-uniform and the harmonic models, which are less conventional but still useable for extracting density distribution properties. Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions. They also rely on a known surface for the asteroid.

@@

As part of our prior, we require that the asteroid density distribution satisfy $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$. This constraint is desirable as it is obeyed for uniform density distributions. To define the prior, we divide the asteroid into $n \gg 1$ small regions of volume $V$, each with position $\bm r_i$ and density $\rho_i = \delta_i + 1$. Setting the mass of the asteroid equal to its volume, the average density is 1, so $\delta_i$ is the difference between the average and local density. We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$, centred on zero to minimize non-uniformity, i.e.
\begin{equation}
  f[\rho(\bm r)] \propto \prod_i \exp\parens{-\frac{\delta_i^2}{2\sigma^2}} \implies \ln f[\rho(\bm r)] \simeq -\sum_i \delta_i^2
  \label{eqn:nu-f}
\end{equation}
where $\sigma$ is an irrelevant constant. The density moments, MOI scale, and mass are 
\begin{equation}
  K_{\ell m} = \frac{V}{\mu_\mathcal{A}a_\mathcal{A}^{\ell}} \sum_i (\delta_i + 1) R_{\ell m}(\bm r_i)
  \label{eqn:nu-klm}
\end{equation}
\begin{equation}
  I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2 = V \sum_i (\delta_i + 1) r_i^2
  \label{eqn:nu-ia}
\end{equation}
\begin{equation}
  \mu_\mathcal{A} = V\sum_i (\delta_i + 1) \implies 0 = \sum_i \delta_i.
  \label{eqn:nu-mass}
\end{equation}
Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$, and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations. Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as 
\begin{equation}
  \bm K = M \bm \delta + \bm C,
  \label{eqn:nu-matrix}
\end{equation}
where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions. Some of the components of $\bm K$, such as $I_\mathcal{A}$, $\mu_\mathcal{A}$, and $K_{1m}$, are constraints. We treat the other components as parameters of the model. The task is then to find $\bm \delta$ that satisfies equation \ref{eqn:nu-matrix} and maximizes $f(\bm \delta)$. But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (also the maximum of $f$) is the minimum of $|\bm \delta|^2$. This shortest value of $\bm \delta$ that obeys equation \ref{eqn:nu-matrix} is given by the Moore-Penrose inverse:
\begin{equation}
  \bm \delta = M^+ (\bm K - \bm C); \qquad M^+ = M^\dagger(M M^\dagger)^{-1}
  \label{eqn:nu-delta}
\end{equation}
where $M^\dagger$ is the adjoint of $M$.

The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
 can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.

\subsection{Harmonic model}
This the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$. We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.

A harmonic density distribution can be expanded in terms of the spherical harmonics as $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*$ where $C_{\ell m}$ are complex, free parameters. This series can be truncated at some maximum $\ell$. The density moments, MOI scale, and mass can then be explicitly computed as a function of $C_{\ell m}$:
\begin{equation}
  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r)
  \label{eqn:harmonic-klm}
\end{equation}
\begin{equation}
  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2
  \label{eqn:harmonic-ia}
\end{equation}
\begin{equation}
  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*.
  \label{eqn:harmonic-mass}
\end{equation}
These integrals can be pre-computed given a known asteroid shape $\mathcal{A}$, so that computing $C_{\ell m}$ to match a given $K_{\ell m}$ is fast. Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions. In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is non-zero only when $\ell' = \ell$ and $m'=m$. Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$. The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics weighted by $K_{\ell m}$. When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to break this picture.

Imposing constraints on these moments is also necessary. The choice of mass is enforced via equation \ref{eqn:harmonic-mass}. We impose bounds on $\rho(\bm r)$ by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid. This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.

To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable. It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity. In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.

\subsection{Uncertainty model}
The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data. This requires a new model for the uncertainty of orientation observations.

For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$. Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as 
\begin{equation}
  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
  \label{eqn:orientation-like}
\end{equation}
where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.

\subsection{Moment uncertainty comparison}
With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets via the fit method defined in the main text. Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets. If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments. However, the relative uncertainty of moments can be compared between the two data sets.

To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets and also compute the mean value of $\sigma(K_{\ell m})$ over all fit parameters. We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set. This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty. The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.

\begin{figure*}
  \centering
  \includegraphics[width=0.75\linewidth]{figs/orientation-unc}
  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data. First order parameters are shown in the left panel and second-order parameters in the right. Mean values are also shown as horizontal lines. Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
  \label{fig:orientation-unc}
\end{figure*}

The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$. This is expected due to the following argument. If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment. Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation. This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly. A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.

\subsection{Density uncertainty comparison}

>>>>

To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable. It is possible that the orientation of the asteroid may be more readily available as a data set. In this appendix, we generate an orientation data set for the reference asteroid flyby, extract density moments from it, and compare the results to moments extracted from angular velocity data.

\subsection{Uncertainty model}
To use an asteroid orientation data set rather than angular velocity, we must create an uncertainty model for orientation observations and produce a likelihood to be used by the MCMC (replacing equation \ref{eqn:log-likelihood}).

For the sake of this appendix, we will assume that all observations of orientation $\quat q$ differ from the true orientation $\quat q^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$. As in the rest of the paper, orientation is expressed as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$. The angle $\phi$ can be extracted from these quaternion components to yield a likelihood of
\begin{equation}
  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
  \label{eqn:orientation-like}
\end{equation}
where a subscript $i$ denotes the $i$th element of the data set. It is assumed that both quaternions have norm one.

\subsection{Moment uncertainty comparison}
With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract density moment PPDs for both data sets via the fit method defined in the main text. Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the amount of moment uncertainty for both data sets. If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments. However, the relative uncertainty of moments can be compared between the two data sets.

To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets. We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set. This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same average precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty. The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figs/orientation-unc}
  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data. First order parameters are shown in the top panel and second-order parameters in the bottom. Mean values are also shown as vertical lines. Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
  \label{fig:orientation-unc}
\end{figure}

The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$, which is much more precisely constrained by orientation data than by angular velocity data. This result is expected due to the following argument. If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment. Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation. That initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so we expect the angular velocity data set to yield increased uncertainties in $\gamma_0$ only, relative to the observational data, to a first approximation.

A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$. However, this has little effect on the density distributions extracted by the finite element model; the average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.

@@

Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints. Here we outline two additional models --- the nearly-uniform and the harmonic models --- which are less conventional but still useable for extracting density distribution properties. Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.

@@

As part of our prior, we require that the asteroid density distribution satisfy $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$. This constraint is desirable as it is obeyed for uniform density distributions. To define the prior, we divide the asteroid into $n \gg 1$ small regions of volume $V$, each with position $\bm r_i$ and density $\rho_i = \delta_i + 1$. Setting the mass of the asteroid equal to its volume, the average density is 1, so $\delta_i$ is the difference between the average and local density. We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$, centred on zero to minimize non-uniformity, i.e.
\begin{equation}
  f[\rho(\bm r)] \propto \prod_i \exp\parens{-\frac{\delta_i^2}{2\sigma^2}} \implies \ln f[\rho(\bm r)] \simeq -\sum_i \delta_i^2
  \label{eqn:nu-f}
\end{equation}
where $\sigma$ is an irrelevant constant. The density moments, MOI scale, and mass are 
\begin{equation}
  K_{\ell m} = \frac{V}{\mu_\mathcal{A}a_\mathcal{A}^{\ell}} \sum_i (\delta_i + 1) R_{\ell m}(\bm r_i)
  \label{eqn:nu-klm}
\end{equation}
\begin{equation}
  I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2 = V \sum_i (\delta_i + 1) r_i^2
  \label{eqn:nu-ia}
\end{equation}
\begin{equation}
  \mu_\mathcal{A} = V\sum_i (\delta_i + 1) \implies 0 = \sum_i \delta_i.
  \label{eqn:nu-mass}
\end{equation}
Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$, and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations. Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as 
\begin{equation}
  \bm K = M \bm \delta + \bm C,
  \label{eqn:nu-matrix}
\end{equation}
where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions. Some of the components of $\bm K$, such as $I_\mathcal{A}$, $\mu_\mathcal{A}$, and $K_{1m}$, are constraints. We treat the other components as parameters of the model. The task is then to find $\bm \delta$ that satisfies equation \ref{eqn:nu-matrix} and maximizes $f(\bm \delta)$. But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (also the maximum of $f$) is the minimum of $|\bm \delta|^2$. This shortest value of $\bm \delta$ that obeys equation \ref{eqn:nu-matrix} is given by the Moore-Penrose inverse:
\begin{equation}
  \bm \delta = M^+ (\bm K - \bm C); \qquad M^+ = M^\dagger(M M^\dagger)^{-1}
  \label{eqn:nu-delta}
\end{equation}
where $M^\dagger$ is the hermitian conjugate of $M$.

The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.

\subsection{Harmonic model}
In the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$. We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.

A harmonic density distribution can be expanded in terms of the spherical harmonics as $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*$ where $C_{\ell m}$ are complex, free parameters. This series can be truncated at some maximum $\ell$. The density moments, MOI scale, and mass can then be explicitly computed as a function of $C_{\ell m}$:
\begin{equation}
  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r)
  \label{eqn:harmonic-klm}
\end{equation}
\begin{equation}
  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2
  \label{eqn:harmonic-ia}
\end{equation}
\begin{equation}
  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*.
  \label{eqn:harmonic-mass}
\end{equation}
Since the integrals are independent of the parameters, they can be computed before solving for $C_{\ell m}$. Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions. In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is non-zero only when $\ell' = \ell$ and $m'=m$. Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$. The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics $R_{\ell m}$ weighted by $K_{\ell m}$. When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to alter this picture.

$C_{\ell m}$ can be treated as parameters for a fitting method (such as an MCMC) that enforces our bounds on $\rho(\bm r)$. With the integrals pre-computed, obtaining $K_{\ell m}$ from $C_{\ell m}$ is fast. We impose these bounds by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid. This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.

### 2022-08-09 paper/main.tex
Done with gamma
Edits to paper

In the following mathematical model for the influence of tidal torque on asteroid encounters, we assume for simplicity that (1) that the central body is much more massive than the asteroid, (2) that both are rigid, (3) that there are no distant perturbing objects and (4) that the asteroid is in a short-axis, non-tumbling rotational state before the encounter. All of these assumptions except 2 can be relaxed without drastic changes to the model.

@@

Since it is the angular acceleration of the asteroid that is observable, rather than the torque applied, we also compute the MOI of the asteroid around the principal axes: 
\begin{equation}
  \begin{split}
    I_x &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} - 6 K_{22} + 1}\\
    I_y &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} + 6 K_{22} + 1}\\
    I_z &= \frac{2}{3} I_\mathcal{A} \parens{-2K_{20} + 1}.
  \end{split}
  \label{eqn:moi}
\end{equation}
Note that all moments of inertia are proportional to $I_\mathcal{A}$. Equation \ref{eqn:tidal-torque} indicated that tidal torque was also proportional to $I_\mathcal{A}$. The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is independent $I_\mathcal{A}$. Thus, the observables do not depend explicitly on $I_\mathcal{A}$.

@@

Moment uncertainty is also affected by $\gamma_0$, which was corrected for in section \ref{sec:scan-orbit}. We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant. Moment uncertainties varied by factors of \jtd{25-100\%}, generally exhibiting roughly sinusoidal behaviour. The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape.

>>>>

In the following mathematical model for the influence of tidal torque on asteroid encounters, we assume for simplicity that (1) the central body is much more massive than the asteroid, (2) both are rigid, (3) there are no distant perturbing objects, and (4) the asteroid is in a short-axis, non-tumbling rotational state before the encounter. All of these assumptions except 2 can be relaxed without drastic changes to the model.

@@

Since it is the angular acceleration of the asteroid that is observable, rather than the torque applied, we also compute the MOI of the asteroid around the principal axes: 
\begin{equation}
  \begin{split}
    I_x &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} - 6 K_{22} + 1}\\
    I_y &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} + 6 K_{22} + 1}\\
    I_z &= \frac{2}{3} I_\mathcal{A} \parens{-2K_{20} + 1}.
  \end{split}
  \label{eqn:moi}
\end{equation}
Note that all moments of inertia are proportional to $I_\mathcal{A}$. Equation \ref{eqn:tidal-torque} indicated that tidal torque was also proportional to $I_\mathcal{A}$. The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is therefore independent $I_\mathcal{A}$. Thus, the observables do not depend explicitly on $I_\mathcal{A}$.

@@

Moment uncertainty is also affected by $\gamma_0$, which was corrected for in section \ref{sec:scan-orbit}. We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant. Moment uncertainties generally varied by factors of two or less, exhibiting roughly sinusoidal behaviour. The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape.
